### 2014-11-12 tex/heap.tex
Fixed the formatting

\subsection{Summary Heaps as Bipartite Graphs}
A novel contribution of summary heaps for symbolic execution is the
labeled bipartite graph representation of the heap which enables a
summary heap to group heaps together that follow the same control flow
to a given point of execution. The graph structure is able to capture
group membership and compute value sets using entirely non-recursive
local look up. Additionally, updates on the heap do not require
rewriting the path condition or any constraints in the heap.

@@

There are several properties of the summary heap 
enforced by the rewrite rules that are invariant and
important to the correctness proofs
presented in \secref{sec:bisim}.

\textbf{Reference partitions}: new references are drawn from
  three distinct partitions (i) $\mathrm{init}_\cfgnt{r}()$ for references for the \emph{input heap}, (ii) $\mathrm{fresh}_\cfgnt{r}()$ for references for \emph{auxiliary literals}, and
  (iii) $\mathrm{stack}_\cfgnt{r}()$ for references for the \emph{stack literals} in the expressions and
  continuations. The references strictly increase in value on each
  call, and modular arithmetic is used to determine the partition to
  which a reference belongs. Reference partitions are a critical piece
  to the existence proof of a bisimulation between the summary heap
  algorithm and generalized symbolic execution (see \secref{sec:bisim}).
\begin{compactitem}
\item \textbf{Input heap}: these references have two
  interpretations: one as a literal and another as a variable. First,
  an input heap reference is a literal, and that literal is a node in
  the summary heap. Second, an input heap reference is a variable, and
  that variable is a term in any number of constraints that label
  edges in the summary heap. Only input heap references and the
  special reference $\cfgnt{r}_\mathit{null}$ appear in constraints
\item \textbf{Auxiliary literals}: these references are only used to define additional structure in
  the bipartite graph and are not part of any constraint and do not appear
  in any environment, expression, or continuation.
\item \textbf{Stack references}: these references are also used to define additional structure in the bipartite graph but may also appear in the environment, expression, or continuation. These are not part of any constraint.
\end{compactitem}

\textbf{Immutable references}: a reference does not change in the
location map. It always points to the same set of constraint location
pairs. This property ensures that constraints never need to be
rewritten as the program evolves its state.

\textbf{Determinism}: a reference in  $(\cfgnt{L}\ \cfgnt{R})$ cannot point multiple locations simultaneously.
$$
\begin{array}{l}
\forall \cfgnt{r} \in \cfgnt{L}^\leftarrow\ (\forall (\phi\ \cfgnt{l}),(\phi^\prime\ \cfgnt{l}^\prime) \in \cfgnt{L}(r)\ (\\
\ \ \ \ (\cfgnt{l} \neq \cfgnt{l}^\prime \vee \phi \neq \phi^\prime) \Rightarrow (\phi \wedge \phi^\prime = \cfgt{false}))
\end{array}
$$
$\cfgnt{L}^\leftarrow$ is the pre-image of the location
map. Informally, any two constraint location pairs connected to a
common reference form a contradiction: only one can be true in any
satisfying assignment. The property means that a satisfying assignment
resolving aliasing relationships results in a deterministic heap: a
field access returns a single location.

\textbf{Type consistency}: all locations associated with a reference have the same type.
\[
\begin{array}{l}
\forall \cfgnt{r} \in \cfgnt{L}^\leftarrow\ (\forall (\phi\ \cfgnt{l}),(\phi^\prime\ \cfgnt{l}^\prime) \in \cfgnt{L}(r)\ (\\
\ \ \ \ (\mathrm{Type}\lp\cfgnt{l}\rp = \mathrm{Type}\lp\cfgnt{l}^\prime\rp)))
\end{array}
\]

\textbf{Null and Uninitialized}: every summary heap contains 
a special location for null ($\cfgnt{l}_\mathit{null}$), and a special
location for uninitialized
  ($\cfgnt{l}_\mathit{un}$), with corresponding references
  $\cfgnt{r}_\mathit{null}$ and
  $\cfgnt{r}_\mathit{un}$, respectively. $\cfgnt{L}(\cfgnt{r}_\mathit{null}) =
  \{(\cfgt{true}\ \cfgnt{l}_\mathit{null})\}$ and
  $\cfgnt{L}(\cfgnt{r}_\mathit{un}) =
  \{(\cfgt{true}\ \cfgnt{l}_\mathit{un})\}$. These special references can be used in constraints.

>>>>

\subsection{Summary Heaps as Bipartite Graphs}
A novel contribution of summary heaps for symbolic execution is the
labeled bipartite graph representation of the heap which enables a
summary heap to group heaps together that follow the same control flow
to a given point of execution. The graph structure is able to capture
group membership and compute value sets using entirely non-recursive
local look up. Additionally, updates on the heap do not require
rewriting the path condition or any constraints in summary heap.

@@

There are several properties of the summary heap enforced by the
rewrite rules that are invariant and important to the correctness
proofs presented in \secref{sec:bisim}: \emph{reference partitions},
\emph{immutable references}, \emph{determinism}, and \emph{type
  consistency}.

Reference partitions: new references are drawn from
  three distinct partitions (i) $\mathrm{init}_\cfgnt{r}()$ for references for the \emph{input heap}, (ii) $\mathrm{fresh}_\cfgnt{r}()$ for references for \emph{auxiliary literals}, and
  (iii) $\mathrm{stack}_\cfgnt{r}()$ for references for the \emph{stack literals} in the expressions and
  continuations. The references strictly increase in value on each
  call, and modular arithmetic is used to determine the partition to
  which a reference belongs.
\begin{compactdesc}
\item[Input heap] these references have two
  interpretations: one as a literal and another as a variable. First,
  an input heap reference is a literal, and that literal is a node in
  the summary heap. Second, an input heap reference is a variable, and
  that variable is a term in any number of constraints that label
  edges in the summary heap. Only input heap references and the
  special reference $\cfgnt{r}_\mathit{null}$ appear in constraints
\item[Auxiliary literals] these references are only used to define additional structure in
  the bipartite graph and are not part of any constraint and do not appear
  in any environment, expression, or continuation.
\item[Stack references] these references are also used to define additional structure in the bipartite graph but may also appear in the environment, expression, or continuation. These are not part of any constraint.
\end{compactdesc}
Reference partitions are a critical piece to the existence proof of a
bisimilation between the summary heap algorithm and generalized
symbolic execution (see \secref{sec:bisim}).

Immutable references: a reference does not change in the
location map. It always points to the same set of constraint location
pairs. This property ensures that constraints never need to be
rewritten as the program evolves its state.

Determinism: a reference in  $(\cfgnt{L}\ \cfgnt{R})$ cannot point multiple locations simultaneously.
$$
\begin{array}{l}
\forall \cfgnt{r} \in \cfgnt{L}^\leftarrow\ (\forall (\phi\ \cfgnt{l}),(\phi^\prime\ \cfgnt{l}^\prime) \in \cfgnt{L}(r)\ (\\
\ \ \ \ (\cfgnt{l} \neq \cfgnt{l}^\prime \vee \phi \neq \phi^\prime) \Rightarrow (\phi \wedge \phi^\prime = \cfgt{false}))
\end{array}
$$
$\cfgnt{L}^\leftarrow$ is the pre-image of the location
map. Informally, any two constraint location pairs connected to a
common reference form a contradiction: only one can be true in any
satisfying assignment. The property means that a satisfying assignment
resolving aliasing relationships results in a deterministic heap: a
field access returns a single location.

Type consistency: all locations associated with a reference have the same type.
\[
\begin{array}{l}
\forall \cfgnt{r} \in \cfgnt{L}^\leftarrow\ (\forall (\phi\ \cfgnt{l}),(\phi^\prime\ \cfgnt{l}^\prime) \in \cfgnt{L}(r)\ (\\
\ \ \ \ (\mathrm{Type}\lp\cfgnt{l}\rp = \mathrm{Type}\lp\cfgnt{l}^\prime\rp)))
\end{array}
\]

Null and Uninitialized: every summary heap contains 
a special location for null ($\cfgnt{l}_\mathit{null}$), and a special
location for uninitialized
  ($\cfgnt{l}_\mathit{un}$), with corresponding references
  $\cfgnt{r}_\mathit{null}$ and
  $\cfgnt{r}_\mathit{un}$, respectively. $\cfgnt{L}(\cfgnt{r}_\mathit{null}) =
  \{(\cfgt{true}\ \cfgnt{l}_\mathit{null})\}$ and
  $\cfgnt{L}(\cfgnt{r}_\mathit{un}) =
  \{(\cfgt{true}\ \cfgnt{l}_\mathit{un})\}$. These special references can be used in constraints.
